%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                 %
%                            APPENDICES                           %
%                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix    % This command is used only once!

% \addcontentsline{toc}{chapter}{APPENDIX}             %toc entry  or:
% \addtocontents{toc}{\parindent0pt\vskip12pt APPENDIX} %toc entry, no page #

% \setcounter{table}{0}
% \renewcommand{\thetable}{A\arabic{table}}

% \setcounter{figure}{0}
% \renewcommand{\thefigure}{A\arabic{figure}}

\chapter{APPENDIX} \label{sec:appendix}

\section{User-Specific Questions}

\begin{enumerate}  
\item Are you affiliated with Rensselaer Polytechnic Institute? 
\item How are you affiliated with Rensselaer Polytechnic Institute?
\item Years of formal education in Architecture?
\item Years of formal education in Visual Arts?
\item Years of job experience in architecture? (including internships) 
\item Years of job experience in Visual Arts? (including internships)
\item Have you used any of the following modeling software?
\begin{enumerate}  
  \item SketchUp
  \item AutoCAD
  \item Rhino
  \item Maya
  \item 3DS Max
  \item Cinema 4D
  \item Blender
  \item Revit
  \item Other
\end{enumerate}
\item Years of experience with modeling software?
\item Other relevant education / experience?
\item Are you colorblind?
\item Is it okay if we follow up with additional questions about specific models you created in our system?
  \begin{enumerate}
    \item If so, please enter your email address
  \end{enumerate}

\item What did you find fun or interesting in this sketching environment?
\item What additional features should be added to system to allow greater flexibility in design?
\item Describe some designs that you were not able to create due  to system limitations?
\item Was there anything you did not like about working in this sketching environment?
\item Where there any UI elements that were hard to use or confusing at first?

\item Describe your overall impression of the software for determining the interior vs exterior space in your designs?
\item For the cases when the system’s interpretation of the interior/exterior of your design was incorrect where was the system wrong? 
\item Did the system allow you to create and test daylighting performance with respect to over or under illumination?

\end{enumerate}

\section{Model-Specific Questions}

\begin{enumerate}
\item What category does this model fall into?
\begin{enumerate}
  \item Dorm
  \item Bedroom
  \item Living room 
  \item Apartment / House
  \item Classroom
  \item Office
  \item Lobby
  \item Other
\end{enumerate}
% If it is an rpi dorm 
\item What dorm is this a model of? (Optional)
\begin{enumerate}
\item BARH (Burdett Avenue Residence Hall)
\item Barton Hall
\item Beman Lane Undergraduate RAHP Apartments
\item Blitman Residence Commons
\item Bray Hall
\item Bryckwyck Floor Plans
\item Cary Hall
\item Colonie Apartments
\item Commons
\item Crockett Hall
\item Davison Hall
\item E-Complex
\item Hall Hall
\item Nason Hall
\item North Hall
\item Nugent Hall
\item Quadrangle (The Quad)
\item Sharp Hall
\item Single RAHP
\item Stacwyck Apartments
\item Warren Hall
\item Other
\end{enumerate}
\item What floor number? (Optional)
\item What room number? (Optional)
\item When was the last time you visited this space? (Optional)
\begin{enumerate}
\item Less than a week ago
\item Less than a month ago
\item Less then a year ago
\item Less than 4 years ago
\item More than 4 years ago
\end{enumerate}
\item How often did you visit this space?
\begin{enumerate}
\item Once
\item Occasionally
\item Multiple times a week
\end{enumerate}
\item How confident are you in modeling this space? (scale of 1 to 5)

\end{enumerate}


\section{Renovation-Specific Questions}
\begin{enumerate}
\item Does the 3D generated model match your intentions?
\begin{enumerate}
\item Matched my intentions exactly ( no revision required )
\item Did not match my intentions initially ( revisions were required )
\item Failed to match my intentions ( even after revision )
\end{enumerate}
\end{enumerate}

\section{Render-Specific Questions}
\begin{enumerate}
\item Did you understand the results of the simulation, was there anything confusing or unclear?
\end{enumerate}
